Data Specialization for a Staged Lambda Calculus

### 2014-11-07 paper/splitting.tex
These are minor grammar edits.

Given a term $e$ in the source language \lang\ where terms of
stage~\bbone\ and stage~\bbtwo\ may be interleaved, \emph{(stage)
  splitting} separates the stage~\bbone\ and stage~\bbtwo\
subcomputations into two terms, $e_1$ and $e_2$, in an unstaged target language \langmono\ 
%each performing the
%subcomputations corresponding to each stage.  More precisely, given a
%\lang\ term~$e$, splitting yields two terms $e_1$ and $e_2$ in a
%unstaged target language \langmono\
such that~$e_1$ performs all the
stage~\bbone\ subcomputations in~$e$ and $e_2$~performs all of the
stage~\bbtwo\ subcomputations. Splitting preserves correctness in the sense that evaluation of~$e$ in
the staged language produces the same result as evaluating~$e_1$, followed by evaluating 
$e_2$ with the result from~$e_1$.

@@

Splitting a stage \bbone\ term $\colone e A$ 
(where $e\mathbin{\redonesym}[\xi;v]$), yields a term 
$e_1$ that performs all stage~\bbone\ subcomputations in $e$ and a \emph{resumer} function $e_2 = l.r$ that represents all stage~\bbtwo\ subcomputations.
For splitting to match the results of evaluating $e$ in \lang,
we require that $e_1$ reduce to the tuple $(y,z)$,
where $y$ is identical to $\masko{\xi;v}$, and 
$\letin l z r$ reduces to the same value as $\maskt{\xi;v}$. Intuitively, $e_1$ performs both the stage~\bbone\ subcomputations needed to produce an \emph{immediate result} $y$, and the stage~\bbone\ subcomputations (\emph{precomputations}) required to produce the input for the resumer.

>>>>

Given a term $e$ in the source language \lang, where terms of
stage~\bbone\ and stage~\bbtwo\ may be interleaved, \emph{(stage)
  splitting} separates the stage~\bbone\ and stage~\bbtwo\
subcomputations into two terms, $e_1$ and $e_2$, in an unstaged target language \langmono\ 
%each performing the
%subcomputations corresponding to each stage.  More precisely, given a
%\lang\ term~$e$, splitting yields two terms $e_1$ and $e_2$ in a
%unstaged target language \langmono\
such that~$e_1$ performs all the
stage~\bbone\ subcomputations in~$e$ and $e_2$~performs all of the
stage~\bbtwo\ subcomputations. Splitting preserves correctness in the sense that evaluation of~$e$ in
the staged language produces the same result as evaluating~$e_1$, followed by evaluating 
$e_2$ with the result from~$e_1$.

@@

Splitting a stage \bbone\ term in \lang\
% $\colone e A$ 
(where $e\mathbin{\redonesym}[\xi;v]$), yields a term 
$e_1$ that performs all stage~\bbone\ subcomputations in $e$ and a \emph{resumer} function $e_2 = l.r$ that performs all stage~\bbtwo\ subcomputations.
For splitting to match the results of evaluating $e$ in \lang,
we require that $e_1$ reduce to the tuple $(y,z)$,
where $y$ is identical to $\masko{\xi;v}$, and 
$\letin l z r$ reduces to the same value as $\maskt{\xi;v}$. Intuitively, $e_1$ performs both the stage~\bbone\ subcomputations needed to produce an \emph{immediate result} $y$, and the stage~\bbone\ subcomputations (called \emph{precomputations}) required to produce the input required by the resumer.
